---
title: "Homework 2"
output:
  pdf_document: default
  html_notebook: default
---

# Recommendation Systems

Let's see our data. 
We have two datasets, the first is a 1,664 movies and all the general information about these movies. 
```{r, echo = FALSE }
library(recommenderlab)
data(MovieLense)  # Not sure why there is an e at the end
MovieLenseMeta
```

The second data set is a matrix of 943 people that have reated these 1,664 movies.  
```{r}
dim(MovieLense)
```

Not all the people rated all the movies. So, as we can see in the following image, rows are users that might or not rate a particular movie (columns). The "scale-color" is the rating per movie.
```{r}
image(MovieLense, main = "Raw ratings")
```


Train Recommendation System
```{r}
train <- MovieLense[1:900]
dim(train) # Using 900 Raters
```

This is a target user, which we would like to recommend. He has a recommended 124 movies. 
```{r}
u <- MovieLense[901] # Score the next one
u
```

Checking out the recommendation methods in this package
```{r, echo= FALSE, eval=FALSE}
# A recommender is created using the creator function Recommender(). 
# Available recommendation methods are stored in a registry.
recommenderRegistry$get_entries(dataType = "realRatingMatrix")
```

Running a User Based Collaborative Filtering
```{r}
r <- Recommender(train, method = "UBCF")
r  # object of type "Recommender"
names(getModel(r))
```


Prediction
```{r}
recom <- predict(r, u, n = 5)
as(recom, "list")
```

## Evaluation
```{r}

scheme <- evaluationScheme(train, 
                           method = "cross", 
                           k = 2,
                           given = 10, 
                           goodRating=3)

algorithms <- list(`random items` = list(name = "RANDOM", param = NULL),
                   `popular items` = list(name = "POPULAR", param = NULL),
                   `user-based CF` = list(name = "UBCF",
                                          param = list(method = "Cosine", nn = 50)),
                   `item-based CF` = list(name = "IBCF",
                                          param = list(method = "Cosine", k = 50)))

results <- evaluate(scheme, algorithms,
                    n = c(1, 5, 10, 15, 50,200,1000))

plot(results, annotate = c(1, 3), legend = "right")
```
















